Project-I by Group Sydney

### 2015-11-01 report/paper.tex
Add Submission

We analyzed a regression data set with different methods and concluded that least squares wasn't a good approach due to the ill-conditioning and the least squares gradient descent was too slow and less efficient than ridge regression. Separation of the data into clusters was essential in order to decrease the test error. Unfortunately, dummy encoding didn't help. However using polynomial basis helped to decrease the bias. Finally, the variance of cluster 1 and 3 are very low, the one for cluster 2 is a bit higher. We think that we have bias because we use ridge regression but we don't think it is too high because we have seen that adding features helps until a certain point. The best model we have is the seventh one and we estimate the \textit{RMSE} of the prediction to be around $115.96$ with a standard deviation of $45.59$. However, we should take into consideration outliers, which gives us a \textit{RMSE} of $407.55$ with a standard deviation of $229.34$. Finally, we think that our model is improvable, however we couldn't try other things to improve the estimation error, due to a lack of time.

>>>>

We analyzed a regression data set with different methods and concluded that least squares wasn't a good approach due to the ill-conditioning and the least squares gradient descent was too slow and less efficient than ridge regression. Separation of the data into clusters was essential in order to decrease the test error. Unfortunately, dummy encoding didn't help. However using polynomial basis helped to decrease the bias. Finally, the variance of cluster 1 and 3 are very low, the one for cluster 2 is a bit higher. We think that we have bias because we use ridge regression but we don't think it is too high because we have seen that adding features helps until a certain point. The best model we have is the seventh one and we estimate the \textit{RMSE} of the prediction to be around $115.34$ with a standard deviation of $454.61$. However, we should take into consideration outliers, which gives us a \textit{RMSE} of $412.52$ with a standard deviation of $234.78$. Finally, we think that our model is improvable, however we couldn't try other things to improve the estimation error, due to a lack of time.
